---
title: "EarAche PubMed"
author: "Janis Corona"
date: "12/9/2019"
output: html_document
---

## This script takes ten articles from the abstracts on earache articles from NCBI's PubMed


This creates a directory to stem the abstracts and preprocess from the csv file
into a corpus of 10 files in a folder called Earache.
```{r}
Auto <- read.csv('NCBI-EarAche-PubMed.csv', sep=',',
                 header=FALSE, na.strings=c('',' '))
colnames(Auto) <- c('abstract','source')

auto <- Auto[complete.cases(Auto$abstract),]


dir.create('./Earache')

ea <- as.character(auto$abstract)
setwd('./Earache')

for (j in 1:length(ea)){
  write(ea[j], paste(paste('EA',j, sep='.'), '.txt', sep=''))
}
setwd('../')


```

This code preprocesses and stems the corpus
```{r, error=FALSE, warning=FALSE, message=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)

Earache <- Corpus(DirSource("Earache"))


Earache

Earache <- tm_map(Earache, removePunctuation)
Earache <- tm_map(Earache, removeNumbers)
Earache <- tm_map(Earache, tolower)
Earache <- tm_map(Earache, removeWords, stopwords("english"))
Earache <- tm_map(Earache, stripWhitespace)
Earache <- tm_map(Earache, stemDocument)

dtmEarache <- DocumentTermMatrix(Earache)

freq <- colSums(as.matrix(dtmEarache))

```

This code orders words stemmed by frequency and finds input correlations
```{r}
FREQ <- data.frame(freq)
ord <- order(freq, decreasing=TRUE)

freq[head(ord, 25)]

findAssocs(dtmEarache, "patient", corlimit=0.5)

```


```{r}
findAssocs(dtmEarache, "ear", corlimit=0.5)

```


```{r}
findAssocs(dtmEarache, "pain", corlimit=0.5)
```


```{r}
wf <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(wf, freq>4), aes(word, freq))
p <- p + geom_bar(stat= 'identity') 
p <- p + theme(axis.text.x=element_text(angle=90, hjust=1)) 
p

```


```{r}
wordcloud(names(freq), freq, min.freq=4,colors=brewer.pal(3,'Dark2'))

```


```{r}
wordcloud(names(freq), freq, max.words=40,colors=brewer.pal(6,'Dark2'))

```

### The above stemmed the corpus, this will lemmatize the original csv file
and add the field to the table and write out to csv, followed by plot the 
word count frequencies that were lemmatized and the word clouds

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(textstem)

lemma <- lemmatize_strings(auto$abstract, dictionary=lexicon::hash_lemmas)

Lemma <- as.data.frame(lemma)
Lemma <- cbind(Lemma, auto)

colnames(Lemma) <- c('lemmatizedAbstract','abstract', 'source')

write.csv(Lemma, 'LemmatizedEarAche.csv', row.names=FALSE)

```

```{r}
dir.create('./EarAche-Lemma')

ea <- as.character(Lemma$lemmatizedAbstract)
setwd('./EarAche-Lemma')

for (j in 1:length(ea)){
  write(ea[j], paste(paste('EAL',j, sep='.'), '.txt', sep=''))
}
setwd('../')

```

```{r, error=FALSE, message=FALSE, warning=FALSE}
library(tm)
library(SnowballC)
library(wordcloud)
library(ggplot2)

```



```{r}
Earache <- Corpus(DirSource("EarAche-Lemma"))

Earache

Earache <- tm_map(Earache, removePunctuation)
Earache <- tm_map(Earache, removeNumbers)
Earache <- tm_map(Earache, tolower)
Earache <- tm_map(Earache, removeWords, stopwords("english"))
Earache <- tm_map(Earache, stripWhitespace)

dtmEarache <- DocumentTermMatrix(Earache)
dtmEarache

```

```{r}
freq <- colSums(as.matrix(dtmEarache))

FREQ <- data.frame(freq)
ord <- order(freq, decreasing=TRUE)

freq[head(ord, 25)]

```


```{r}
patient <- as.data.frame(findAssocs(dtmEarache, "patient", corlimit=0.6))

earache <- as.data.frame(findAssocs(dtmEarache, "earache", corlimit=0.55))


treatment <- as.data.frame(findAssocs(dtmEarache, "treatment", corlimit=0.55))

patient
earache
treatment
```

```{r, width=500, height=500}
wf <- data.frame(word=names(freq), freq=freq)
p <- ggplot(subset(wf, freq>4), aes(word, freq))
p <- p + geom_bar(stat= 'identity') 
p <- p + theme(axis.text.x=element_text(angle=90, hjust=1)) 
p

```

```{r}
wordcloud(names(freq), freq, min.freq=5,colors=brewer.pal(3,'Dark2'))

```

```{r}
wordcloud(names(freq), freq, max.words=40,colors=brewer.pal(6,'Dark2'))

```

